Improving the Replicability of Psychological Science Through Pedagogy

### 2016-09-23 paper/paper.Rmd
Fix legend order
Compile large SOM plot

Next, following @etz2016, we compared Bayes Factors between the original and replication. We used the default test suggested by @rouder2009 and did not attempt to correct for publication bias.^[A default BF for one paper could not be computed based on the statistical test that was used.] This analysis revealed a number of interesting findings. First, as with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals. Second, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments. Finally, the Bayes Factors for several of the original effects did not appear to show strong evidential value (e.g., BF < 3, indicating that the alternative hypothesis is more than three times more likely than the null); it would have been somewhat surprising for our replications to show stronger evidence than the original.

@@

p2 <- ggplot(tstatDF, aes(x = origBF, y = repBF)) +
  geom_point(alpha = .8, aes(size = df_ratio, 
                             col = replicated_TA_factor)) +
  geom_abline(slope = 1, lty = 2) + 
  geom_smooth(method = "lm", se=FALSE) +
  # geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
  xlab("Orig. Bayes Factor") + 
  ylab("Rep. Bayes Factor") + 
  scale_x_log10(limits = c(10**-1.75, 10**11), 
                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c(".1", "1", "10","100", "1e3", 
                           "1e6","1e9")) +
  scale_y_log10(limits = c(10**-1.75, 10**11),
                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c(".1", "1", "10","100", "1e3", 
                           "1e6","1e9")) + 
  theme_bw(base_size=10) + theme(legend.position="bottom") + 
    scale_size_continuous(breaks=c(.5, 2, 5),name = "rep. df/orig. df") + 
  scale_color_solarized(name = "Subj. rep. rating")

@@

```{r, fig.height=9, fig.width=6, fig.cap="Side-by-side plots for each attempted replication. Error bars show standard error of the mean. Original data estimated from figures when not otherwise available. Replications are sorted by subjective replication success."}
  # colors:268bd2 859900 dc322f
library(png)
layout(matrix(1:24,nr=6,byr=T))
project_key_sorted <- c(
  "jsalloum","ehermann","salehi", # rep = 1
  "mkeil","smraposo","jedtan","rhiac","lampinen", # rep=.5
  "jreynolds","jmarias","auc" #rep = 0
)
for (key in project_key_sorted) {
  orig <- readPNG(paste0("../figures/",key,"-original.png"))
  rep <- readPNG(paste0("../figures/",key,"-replication.png"))

>>>>

Next, following @etz2016, we compared Bayes Factors between the original and replication. We used the default test suggested by @rouder2009 and did not attempt to correct for publication bias.^[A default BF for one paper could not be computed based on the statistical test that was used.] This analysis revealed a number of interesting findings. First, as with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals. Second, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments. Finally, the Bayes Factors for several of the original effects did not appear to show strong evidential value (e.g., BF < 3); it would have been somewhat surprising for our replications to show stronger evidence than the original.

@@

p2 <- ggplot(tstatDF, aes(x = origBF, y = repBF)) +
  geom_point(alpha = .8, aes(size = df_ratio, 
                             col = replicated_TA_factor)) +
  geom_abline(slope = 1, lty = 2) + 
  geom_smooth(method = "lm", se=FALSE) +
  # geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
  xlab("Orig. Bayes Factor") + 
  ylab("Rep. Bayes Factor") + 
  scale_x_log10(limits = c(10**-1.75, 10**11), 
                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c(".1", "1", "10","100", "1e3", 
                           "1e6","1e9")) +
  scale_y_log10(limits = c(10**-1.75, 10**11),
                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c(".1", "1", "10","100", "1e3", 
                           "1e6","1e9")) + 
  theme_bw(base_size=10) + theme(legend.position="bottom") + 
  scale_size_continuous(name = "rep. df/orig. df") + 
  scale_color_solarized(name = "Subj. rep. rating")

@@

```{r, fig.height=9, fig.width=6, fig.cap="Side-by-side plots for each attempted replication. Error bars show standard error of the mean. Original data estimated from figures when not otherwise available."}
  # colors:268bd2 859900 dc322f
library(png)
layout(matrix(1:24,nr=6,byr=T))
project_key_sorted <- c("ehermann", "jsalloum", "smraposo", "jedtan", "salehi", "jreynolds","auc","mkeil","jmarias","lampinen","rhiac") #alphabetical by author

for (key in project_key_sorted) {
  orig <- readPNG(paste0("../figures/",key,"-original.png"))
  rep <- readPNG(paste0("../figures/",key,"-replication.png"))
